---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path='figures/')
```
addig some additioal text
## Loading and preprocessing the data
```{r dataload}
library('dplyr')
activity <- read.csv("activity.csv")
good <- complete.cases(activity)
activity_NA <- activity[!good, ]
activity <- activity[good, ]
```

## What is mean total number of steps taken per day?
```{r task1}
activity_day <- transmute(activity, steps = steps, day = as.Date(date))
activity_group_day <- group_by(activity_day, day)
activity_summary_day <- summarize(activity_group_day, total = sum(steps), Mean = mean(steps), Median = median(steps))
hist(activity_summary_day[[2]], main = 'Frequecy of Number of Steps', col = 'Red', xlab = 'Number of Steps', ylim = c(0, 30))
print.data.frame(transmute(activity_summary_day, Day = day, Mean = Mean, Median = Median), row.names=FALSE)
```
The median values are all . This is because most of the itervalls per day do have 0 steps.
## What is the average daily activity pattern?
```{r task2 }
activity_group_interval <- group_by(activity, interval)
activity_summary_interval <- as.data.frame(summarize(activity_group_interval, Mean = mean(steps)))
plot(activity_summary_interval, type = 'l')
max_mean_steps <- activity_summary_interval[activity_summary_interval$Mean == max(activity_summary_interval$Mean), ]$interval
```
The maximum number of steps is `r max_mean_steps`. 

## Imputing missing values
```{r task 4}
num_row <- nrow(activity_NA)
for(i in 1:nrow(activity_NA)){
        steps <- activity_summary_interval[activity_summary_interval$interval == activity_NA[i, ]$interval, ]$Mean
        activity_NA[i, ]$steps <- steps
}

activity_new <- rbind(activity, activity_NA)

activity_new_day <- transmute(activity_new, steps = steps, day = as.Date(date))
activity_new_group_day <- group_by(activity_new_day, day)
activity_new_summary_day <- summarize(activity_new_group_day, total = sum(steps), Mean = mean(steps), Median = median(steps))

hist(activity_new_summary_day[[2]], main = 'Frequecy of Number of Steps', col = 'Red', xlab = 'Number of Steps', ylim = c(0, 30))
print.data.frame(transmute(activity_new_summary_day, Day = day, Mean = Mean, Median = Median), row.names=FALSE)
```
The total number of entries with missing values is `r num_row`.
The overall pattern of the activities hs not chaged. The number of steps has icreased, because i added the mean of the intervall to the missig values. This is also the reson why the median is now differnt from 0.


## Are there differences in activity patterns between weekdays and weekends?
```{r task 5}
weekend <- c('Saturday', 'Sunday')
activity_week <- transmute(activity_new, steps = steps, interval = interval, wday = as.factor(weekdays(as.Date(date))))
activity_week_end <- transmute(activity_week, steps = steps, interval = interval, weekend = as.factor(wday %in% weekend))

activity_weekend <- subset(activity_week_end, weekend == TRUE, select = c(steps, interval))
activity_weekday <- subset(activity_week_end, weekend == FALSE, select = c(steps, interval))

activity_group_interval_wd <- group_by(activity_weekday, interval)
activity_summary_interval_wd <- as.data.frame(summarize(activity_group_interval_wd, Mean = mean(steps)))

activity_group_interval_we <- group_by(activity_weekend, interval)
activity_summary_interval_we <- as.data.frame(summarize(activity_group_interval_we, Mean = mean(steps)))

plot(activity_summary_interval_wd, type = 'l', col = 'green')
lines(activity_summary_interval_we, col = 'red')
#egend("topright", pch = '-', col = c('black', 'red', 'blue'), legend = c('Sub_metering_1','Sub_metering_2','Sub_metering_3'))
#print.data.frame(transmute(activity_new_summary_day, Day = day, Mean = Mean, Median = Median), row.names=FALSE)
```